
```{r, include = FALSE}
source(here("day1/src/global.R"))
library(mrgsolve)
library(dplyr)
library(knitr)
library(lattice)
tryit_file <- "workbook.Rmd"
```

```{r echo = FALSE, message = FALSE}
mod <- mread_cache("pk1", modlib()) %>% 
  update(end = 192, delta = 0.2) %>% Req(CP)
data(exidata)
data <- filter(exidata, ID <=10)
set.seed(1222)
```

# Where did <red>mod</red> come from?

```{r, eval = FALSE}
mod <- mread("simple", "model")
```


```{r, eval = FALSE}
mod <- mread("<model-name>", "<project-directory>")
```

- By default mrgsolve looks for the code in the file
    - <grn>model-name.cpp</grn> in
    - <blu>project-directory</blu>

- <red>mread demo</red>

```{r, echo = FALSE}
Sys.sleep(2)
```


# Read in a model object with caching {.drop}

First time to read
```{r, include = FALSE, message = FALSE}
mod <- mread("simple", here("day1/model"), preclean = TRUE, compile = FALSE)
```


```{r, message = TRUE}
mod <- mread_cache("simple", here("day1/model"))
```

Next time to read

```{r, message = TRUE}
mod <- mread_cache("simple", here("day1/model"))
```

# Model build directory (`soloc`)

It can be helpful to set

```{r, eval=FALSE}
options(mrgsolve.soloc = "my_build_directory")
```

Equivalent to 

```{r,eval=FALSE}
mod <- mread("simple", here("day1/model"), soloc = "my_build_directory")
```

# Internal model library

```{r, eval = FALSE}
mod <- mread("<first-argument>", "<second-argument>")
```

# Internal model library

```{r, eval = FALSE}
mod <- mread("<first-argument>", "<second-argument>")
```

```{r, eval = FALSE}
mod <- mread("<first-argument>", modlib())
```

```{r}
modlib()
```


# Internal model library
```{r}
mod <- mread("effect", modlib())
```

```{r}
mod
```



# Try this now

Open R script in Rstudio then ...

```{r, eval = FALSE}
library(mrgsolve)
```


```{r,eval=FALSE}
mod <- mread("pbpk", modlib())
```


```{r}
mod <- modlib("pbpk")
```

# <red>Your turn</red>

- File name: <grn>day1/exercises/warm_up.R</grn>

- Section name: <blu>Warm Up</blu>

